---
title: ' Sentiment Analysis on Text data'
author: "Uche Kalu"
date: "4/17/2022"
output:
  pdf_document: default
  html_document: default
editor_options:
  markdown:
    wrap: 72
---

### Sentiment Analysis on Tweet and Tweet-related information of Apple company

**Sentiment Analysis or Opinion Mining is a Natural Language Processing
(NLP) technique that is performed on textual data to help businesses
monitor brand and product sentiment in customer feedback, and understand
customer needs.**

**It is used to determine whether data is positive, negative or
neutral**

```{r include=FALSE}
library(syuzhet)         
library(lubridate)
library(ggplot2)
library(scales)
library(reshape2)
library(dplyr)
```

### DATA

```{r save, message=FALSE, warning=FALSE}
mydata <- read.table("apple.txt", header = T, sep = ',')

ourdata <- iconv(mydata$text, to = "UTF-8")
```

### Obtain Sentiment scores for each Tweet

**This will classify all the indexed tweets (each tweet will have an
index number) among multiple sentiment column that best fits/describes
that tweet**

**Lets see the first 6 tweets and their Sentiment scores/values**

```{r message=FALSE, warning=FALSE}
s <- get_nrc_sentiment(ourdata)   
head(s) 
```

**Lets see the 4th tweet that contains all this sentiments**

```{r}
ourdata[4]     

```

**Lets see the 1st tweet that contains all this sentiments**

```{r}
ourdata[1]
```

**We will classify the stated word - delay (taken from a tweet) among
the multiple sentiment column headers that best fits/describes the
stated word**

```{r}
get_nrc_sentiment('delay') 

```

**We will classify the stated word - ugly (taken from a tweet) among the
multiple sentiment column headers that best fits/describes the stated
word**

```{r}
get_nrc_sentiment('ugly')
```

### Visualizing the Sentiments Scores

**Create a Bar plot using the Sentiment Scores**

```{r fig.width=10}
barplot(colSums(s),
        las = 2,             
        col = rainbow(10),    
        ylab = 'Count',
        main = 'Sentiment Scores for Apple Tweets')
```

**Lets display the Sentiment scores by percentage value**

```{r fig.width=10}
we <- 100*colSums(s)/sum(s)   

barplot(we,   
        las = 2,             
        col = rainbow(10),    
        ylab = 'Count',
        main = 'Sentiment Scores for Apple Tweets')
```
